---
title: "Graphics  to share"
author: "Cochet"
date: "11/01/2021"
output:
  beamer_presentation: default
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r mtcars, echo = TRUE}
summary(mtcars)
```

## Slide with Plot

```{r mpg vs cyl}
plot(x = mtcars$cyl, y = mtcars$mpg)
```

## Slide with Linear Model

```{r lm, include = TRUE}
fit <- lm(mpg ~ cyl, data = mtcars)
mtcars$am <- factor(mtcars$am)
plot(mtcars$am, mtcars$mpg, xlab="Transmission type",ylab="mpg")
mtext("Transmission (0 = automatic, 1 = manual)")
print(fit$coefficients)
```